Fundamental Problems with Child and Adolescent Depression Treatments

### 2024-04-19 Manuscript_for_rendering_in_word.qmd
Lots of formatting things, success in fixing up tables Next to address are issues with the figures

---
title: "Fundamental Problems with Child and Adolecsent Depression Treatments: A Quantitative Reappraisal of the Evidence Base"
author:
  - name: Argyris Stringaris
    email: a.stringaris@ucl.ac.uk
    affiliations: 
        - id: ucl_1
          name: University College London
          department: Divisions of Psychiatry and Psychology and Language Science
          address: 1-19 Torrington Place
          city: London, UK
          state: 
          postal-code: WC1E 7HB
          country: United Kingdom
    attributes:
        corresponding: true
    note: 
  - name: Charlotte Burman
    email: charlotte.burman@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Dayna Bhudia
    email: dayna.bhudia@ucl.ac.uk
    affiliations:
        - ref: ucl_1
  - name: Despina Miliou
    email: dgmiliou@outlook.com.gr
    affiliations:
        - ref: ucl_1
  - name: Giannis Rokas
    email: <rokasgiannis93@gmail.com
    affiliations:
        - ref: ucl_1
  - name: Lucy Foulkes
    email: lucy.foulkes@psych.ox.ac.uk
    affiliations:
        - id: OU
          name: University of Oxford
          department: Experimental Psychology
          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
          city: Oxford
          postal-code: OX2 6GG
          country: United Kingdom
    note:
  - name: Carmen Moreno
    email: cmoreno@hggm.es
    affiliations:
        - id: HGM
          name: Hospital Gregorio Marañón
          department: Department of Psychiatry
          address: 46 C. del Dr. Esquerdo
          city: Madrid
          state:
          postal-code: 28007
          country: Spain
  - name: Samuele Cortese
    email: samuele.cortese@soton.ac.uk
    affiliations:
        - id: soton
          name: University of Southampton
          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
          address: Highfield Campus, Building 44
          city: Southampton
          state:
          postal-code: SO17 1BJ
          country: United Kingdom
  - name: Georgina Krebs
    email: g.krebs@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
keywords: 
  - depression
  - adolescents
  - antidepressants
  - psychotherapy
date: last-modified

format: docx
editor: visual
bibliography: "emotion_concepts_paper.bib"
font:
  family: "Calibri"
---

@@

###########Libraries needed
library(tidyverse)
library(truncnorm)
library(metafor)
library(meta)
library(kableExtra)
library(flextable)
library(magrittr)
library(officer)
library(RefManageR)
library(ftExtra)

@@

  # Plotting
  plot_means <- ggplot(dataframe, aes(x = coef_means, y = 1:nrow(dataframe),
                                      colour = condition, label = text_label)) +
    geom_point(label=dataframe$k) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
    geom_text(vjust = +1.5, size = 4) +
    scale_size_continuous(guide = "none") +
    guides(colour = FALSE) + 
    scale_color_manual(values = c(redish_palette, blueish_palette)) +
    theme_minimal() +
    labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
         subtitle = subtitle) +
    xlab("Standardized Mean Difference (SMD) with 95% CIs") +
    ylab("") +
    ylim(0, nrow(dataframe) + 1) +
    xlim(-3.0, 0.5) +
    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
    theme(axis.title.x = element_text(size = 12), 
          axis.text.x  = element_text(size = 12),
          axis.text.y = (element_blank()),
          plot.title = element_text(size = 12),
          plot.subtitle = element_text(size = 12)) +
    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey", vjust = 0.5, hjust = 0)

@@

#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
```

# Results

@@

# add the ns
df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))

@@

# add the ns to the dataframe
 coef_and_se_means_cbt_fluox_esc_study$n  <- study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing ==F,]$n

@@

coef_and_se_means_no_wl$n <- study_count_no_wl_study[study_count_no_wl_study$is_missing 
                                                     ==FALSE,]$n

@@

# add the ns to the dataframe
coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n

@@

# add the ns to the dataframe
coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n

@@

**Table 1**: Sample characteristics at baseline across medication and psychotherapy studies
```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Start by looking at demographics at baseline
# Currently we have both control and active conditions, we just need each study once

@@

# Too basic, limited formatting options
# 
# knitr:: kable(df_overall_baseline_results, caption="Sample characteristics at baseline across medication and psychotherapy studies")
# 
# gt(df_overall_baseline_results) %>%
#   tab_header(
#     title = md("Test this"),
#     subtitle = md("And this"))
# 
# This doesn't work when rendering to word doc
# 
#   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
#   row_spec(row = 1, bold = T) %>%
#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
#   column_spec(1, border_right = T) %>%
#   add_indent(c(2, 3, 5, 6, 8, 9))
# 
# this doesn't have a caption when rendering to word
# 
# flextable(df_overall_baseline_results) %>%
#   set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
#   bold(part = "header") %>%  # Bold the header row
#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
#   border_outer(border = small_border) %>%  # Add outer borders
#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>%
#   hline(part = "header", border = big_border) %>%
#   vline(j = 1, border = big_border) %>%
#   set_table_properties(width = .75) %>%  # Set table width
#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
#   autofit() %>%  # Autofit column widths
#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>%
#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

@@

df_overall_baseline_results <- df_overall_baseline_results %>% 
  mutate(category = case_when(
    row_number() %in% 1:9 ~ "Baseline Severity",
    row_number() %in% 10:18 ~ "Percent Female",
    row_number() %in% 19:27 ~ "Age",
    TRUE ~ ""
  )) %>% # grouping rows
  group_by(category) %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(values = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% 
  set_caption("Table 1: Sample characteristics at baseline across medication and psychotherapy studies") %>%
  bold(part = "header") %>%  # Bold the header row
  bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  border_outer(border = small_border) %>%  # Add outer borders
  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(part = "header", border = big_border) %>%
  vline(j = 1, border = small_border) %>%
  set_table_properties(width = .75) %>%  # Set table width
  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% 
  autofit() %>%  # Autofit column widths
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>%
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>%

df_overall_baseline_results

@@

colnames(sites_t_test_stats) <- c("Statistic", "df", "p-value", "Lower CI", "Upper CI")

# scatter plot

# ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
#   geom_point(position = position_jitter(width = 0.2), size = 2) +
#   labs(title = "Number of Sites for Psychotherapy and Medication Trials",
#        x = "Treatment Modality",
#        y = "Number of Sites") +
#   scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))

# Create a flextable object

flextable(df_sites_summary_stats) %>%
  set_caption ("Table 2: Number of sites across medication and psychotherapy studies") %>%
  bold(part = "header") %>%
  border_outer(border = small_border) %>%
  hline(part = "all", border = small_border) %>%
  hline(part = "header", border = big_border) %>%
  vline(j = 1, border = small_border) %>%
  set_table_properties(width = .75) %>%
  bg(bg = "#F2F2F2", part = "header") %>%
  autofit() %>%
  font(fontname = "Calibri", part = "all") %>%
  padding(i = c(1, 2), j = 1, padding.left = 10) %>%
  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all")

flextable(sites_t_test_stats) %>%
  set_caption ("Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(align = "center", part = "all")

@@

There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3. Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`). Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.

@@

As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms. In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 4 below).

@@

subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
#print(plot_means_all)
pdf(file = "plot_means_all.pdf")
# Instead of PDF
png(file = "plot_means_all.png")
dev.off()

@@

df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition))) %>% 
  relocate("n", .after = "condition")

@@

# Assign new column names to the data frame
colnames(df_mean_coefs_from_sim) <- new_column_names

@@

flextable(df_mean_coefs_from_sim) %>%
  set_caption ("Summary statistics of the estimated SMDs") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center")

@@

![Figure 1.](plot_means_all.png)

@@

In Table 5, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls. In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared. The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).

@@

#aggregate_results_overall

flextable(aggregate_results_overall) %>%
  set_caption ("Metaregression results") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(aggregate_results_overall), align = "center")

@@

We then conducted a series of sensitivity analyses of our results.First, we analysed the data after excluding waitlist control studies. As can be seen, the pattern of results is very similar to that of the overall analyses.

@@

@@

>>>>

---
title: "Fundamental Problems with Child and Adolescent Depression Treatments"
subtitle: "A Quantitative Reappraisal of the Evidence Base"
author:
  - name: Argyris Stringaris
    email: a.stringaris@ucl.ac.uk
    affiliations: 
        - id: ucl_1
          name: University College London
          department: Divisions of Psychiatry and Psychology and Language Science
          address: 1-19 Torrington Place
          city: London, UK
          state: 
          postal-code: WC1E 7HB
          country: United Kingdom
    attributes:
        corresponding: true
    note: 
  - name: Charlotte Burman
    email: charlotte.burman@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Dayna Bhudia
    email: dayna.bhudia@ucl.ac.uk
    affiliations:
        - ref: ucl_1
  - name: Despina Miliou
    email: dgmiliou@outlook.com.gr
    affiliations:
        - ref: ucl_1
  - name: Giannis Rokas
    email: <rokasgiannis93@gmail.com
    affiliations:
        - ref: ucl_1
  - name: Lucy Foulkes
    email: lucy.foulkes@psych.ox.ac.uk
    affiliations:
        - id: OU
          name: University of Oxford
          department: Experimental Psychology
          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
          city: Oxford
          postal-code: OX2 6GG
          country: United Kingdom
    note:
  - name: Carmen Moreno
    email: cmoreno@hggm.es
    affiliations:
        - id: HGM
          name: Hospital Gregorio Marañón
          department: Department of Psychiatry
          address: 46 C. del Dr. Esquerdo
          city: Madrid
          state:
          postal-code: 28007
          country: Spain
  - name: Samuele Cortese
    email: samuele.cortese@soton.ac.uk
    affiliations:
        - id: soton
          name: University of Southampton
          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
          address: Highfield Campus, Building 44
          city: Southampton
          state:
          postal-code: SO17 1BJ
          country: United Kingdom
  - name: Georgina Krebs
    email: g.krebs@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
keywords: 
  - depression
  - adolescents
  - antidepressants
  - psychotherapy
date: last-modified
format:
  docx:
    reference-doc: custom-reference-doc.docx
editor: visual
bibliography: "emotion_concepts_paper.bib"
font:
  family: "Calibri"
---

@@

###########Libraries needed
library(tidyverse)
library(truncnorm)
library(metafor)
library(meta)
library(kableExtra)
library(flextable)
library(magrittr)
library(officer)
library(RefManageR)
library(ftExtra)
library(dplyr)

@@

  # Plotting
  plot_means <- ggplot(dataframe, aes(x = coef_means, y = 1:nrow(dataframe),
                                      colour = condition, label = text_label)) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
    geom_text(vjust = +1.5, size = 4) +
    scale_size_continuous(guide = "none") +
    guides(colour = FALSE) + 
    scale_color_manual(values = c(redish_palette, blueish_palette)) +
    theme_minimal() +
    labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
         subtitle = subtitle) +
    xlab("Standardized Mean Difference (SMD) with 95% CIs") +
    ylab("") +
    ylim(0, nrow(dataframe) + 1) +
    xlim(-3.0, 0.5) +
    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
    theme(axis.title.x = element_text(size = 12), 
          axis.text.x  = element_text(size = 12),
          axis.text.y = (element_blank()),
          plot.title = element_text(size = 12),
          plot.subtitle = element_text(size = 12)) +
    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey", vjust = 0.5, hjust = 0)

@@

#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave

```
# Results

@@

# add the ns
df_mean_coefs_from_sim <- left_join(df_mean_coefs_from_sim, df_count_studies[df_count_studies$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")

@@

# add the ns to the dataframe
coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")

@@

coef_and_se_means_no_wl <- left_join(coef_and_se_means_no_wl, study_count_no_wl_study[study_count_no_wl_study$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")

@@

# add the ns to the dataframe
coef_and_se_means_cdrs_study <- left_join(coef_and_se_means_cdrs_study, study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")

@@

# add the ns to the dataframe
coef_and_se_means_clin_study <- left_join(coef_and_se_means_clin_study, study_count_clin_study[study_count_clin_study$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Start by looking at demographics at baseline
# Currently we have both control and active conditions, we just need each study once

@@

# Too basic, limited formatting options
# 
# knitr:: kable(df_overall_baseline_results, caption="Sample characteristics at baseline across medication and psychotherapy studies")
# 
# gt(df_overall_baseline_results) %>%
#   tab_header(
#     title = md("Test this"),
#     subtitle = md("And this"))
# 
# This doesn't work when rendering to word doc
# 
#   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
#   row_spec(row = 1, bold = T) %>%
#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
#   column_spec(1, border_right = T) %>%
#   add_indent(c(2, 3, 5, 6, 8, 9))
# 
# this doesn't have a caption when rendering to word. workaround below, adding caption as header row.
# 
# flextable(df_overall_baseline_results) %>%
#   set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
#   bold(part = "header") %>%  # Bold the header row
#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
#   border_outer(border = small_border) %>%  # Add outer borders
#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>%
#   hline(part = "header", border = big_border) %>%
#   vline(j = 1, border = big_border) %>%
#   set_table_properties(width = .75) %>%  # Set table width
#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
#   autofit() %>%  # Autofit column widths
#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>%
#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

@@

df_overall_baseline_results %>% 
  mutate(category = case_when(
    row_number() %in% 1:9 ~ "Baseline Severity",
    row_number() %in% 10:18 ~ "Percent Female",
    row_number() %in% 19:27 ~ "Age",
    TRUE ~ ""
  )) %>% # grouping rows
  group_by(category) %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  paginate(group = "category", group_def = "rle") %>% 
  bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width
  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
  autofit() %>%  # Autofit column widths
  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>% # indent some rows
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
  add_header_row(values = "Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% # This is a work around for the problems with rendering captions
  add_header_row(values = "Table 1", colwidths = 8) %>% 
  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(i = 3, part = "header", border = big_border) %>% 
  padding(i = 2, padding.bottom = 15, part = "header") %>% 
  line_spacing(space = .7, part = "all")

@@

flextable(df_sites_summary_stats) %>%
  set_table_properties(width = 1, layout = "autofit") %>%
  add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
                      "; ", as_i("p "), sites_t_test_stats$p_value, 
                      "; 95% CI: ", sites_t_test_stats$ci_lower,
                      "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
  add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
  add_header_row(values = "Table 2", colwidths = 4) %>% 
  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(i = 3, part = "header", border = big_border) %>% 
  padding(i = 2, padding.bottom = 15, part = "header") %>%
  padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>% 
  autofit() %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")

@@

There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Table 2. Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`). Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.

@@

As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms. In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 3 below).

@@

subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
pdf(file = "plot_means_all.pdf")

@@

table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition))) %>% 
  relocate("n", .after = "condition")

@@

# Assign new column names to the data frame
colnames(table_mean_coefs_from_sim) <- new_column_names

@@

flextable(table_mean_coefs_from_sim) %>%
  set_table_properties(width = 1, layout = "autofit") %>%
  autofit() %>%
  font(fontname = "Calibri", part = "all") %>% 
  add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
  add_header_row(values = "Table 3", colwidths = 6) %>% 
  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(i = 3, part = "header", border = big_border) %>% 
  padding(i = 2, padding.bottom = 15, part = "header") %>% 
  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")

@@

![Figure 1.](plot_means_all.pdf)

@@

In Table 4, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls. In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared. The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).

@@

table_aggregate_results_overall <- aggregate_results_overall[, 1:6]

flextable(table_aggregate_results_overall) %>%
  set_table_properties(width = 1, layout = "autofit") %>%
  autofit() %>%
  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
  add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
  add_header_row(values = "Table 4", colwidths = 6) %>% 
  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(i = 3, part = "header", border = big_border) %>% 
  padding(i = 2, padding.bottom = 15, part = "header") %>% 
  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")

@@

We then conducted a series of sensitivity analyses of our results. First, we analysed the data after excluding waitlist control studies. As can be seen, the pattern of results is very similar to that of the overall analyses.

@@

Finally, we examined the data including only those studies that used the CDRS, which yielded a very similar pattern of results.

subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study, subtitle_text_cdrs)
pdf(file = "plot_means_cdrs.pdf")
plot_means_cdrs
dev.off()

![](plot_means_cdrs.pdf)

@@

# References
